---
title: "Marketing Access Scorecard"
subtitle: "Proposal Presentation"
author: "Roxana Rodriguez"
institute: "IBM 6400, Cal Poly Pomona"
format: 
  revealjs:
    theme: serif
    width: 1600
    height: 900
    footer: MSDM CEP
    transition: slide
    transition-speed: default
    incremental: false
    toc: true
    toc-depth: 1
    slide-number: true
    scrollable: true
    smaller: true
    code-fold: true
    code-overflow: wrap
    number-sections: false
    number-depth: 5
    embed-resources: true
    css: styles.css
editor: visual
execute: 
  echo: true
  freeze: auto
---

## Table of Contents

1.  Competitor Analysis
2.  Investigation of Currently Available Research Framework/Model
3.  Measures
4.  Analytics Methods to Employ
5.  Variables to Be Used
6.  Keyword Research Analysis

## **Competitive Analysis**

::: {.fragment .fade-up}
**Competitor #1: Bold Culture** - DEI consulting for internal + external brand efforts.

-   Positions as a company improving inclusive marketing & workplace culture.

-   Website with services, reports, case studies.

-   SEO targeting “inclusive consultancy,” “inclusive marketing.”

-   Facebook, LinkedIn, Instagram.

-   No paid ads, influencer marketing, or affiliate activity.
:::

::: {.fragment .fade-up}
**Competitor #2: Touchstone Research**

-   Multicultural qualitative & quantitative research.

-   Targets entertainment, apparel, and food industries.

-   Positions as an inclusive research partner.

-   Website with dedicated service pages, industry pages, testimonials.

-   SEO with targeted keywords (e.g., UX research, quant research).

-   LinkedIn, YouTube (limited activity).

-   No paid advertising or expanded digital tactics.

-   Email marketing + LinkedIn.

-   No paid ads or influencer efforts.
:::

## **Competitive Analysis**

::: {.fragment .fade-up}
**Competitor #3: C+R Research (CultureBeat)**

-   Cultural insights subdivision focused on diverse audiences.

-   Positions as an analytics + cultural strategy partner.

-   Strong website UX (videos, CTAs, lead forms).

-   Blog, guides, events, webinars.

-   Email marketing + LinkedIn.

-   No paid ads or influencer efforts.
:::

## **Investigation of Currently Available Research Framework/Model**

**Analytics Objective #3: Conduct keyword-research analysis and explore GA4 data from the MAS website** to generate insights for SEO optimization, landing-page usability improvements, and content-engagement optimization.

::: {.fragment .fade-up}
**Existence of Well-Established Models**

-   *Digital Marketing Capability Model (DMC):* Websites as data-driven lead tools.

-   *Commitment-Trust Theory:* Builds credibility and long-term B2B relationships.

-   *Koch and Hartmann (2022):*Navigation, trust, and design affect buyer intention.

-   *Elaboration Likelihood Model (ELM):*

    -   Peripheral: Visual cues for trust.

    -   Central: Deep processing of case studies + findings.

-   *AIDA Model:* Guides users from attention → action (downloads, inquiries).
:::

## **Investigation of Currently Available Research Framework/Model**

::: {.fragment .fade-up}
**Need for Additional Analysis**

-   Conduct surveys to measure perceptions of inclusive marketing.

-   Perform sentiment analysis to understand what messaging resonates with B2C brands.

-   After launch, analyze GA4 metrics to refine content, SEO, and design.
:::

::: {.fragment .fade-up}
**Adequateness of Gathered Information**

-   Current research supports that UX, content quality, and social proof improve B2B engagement.

-   Literature Insights align with MAS goals of educating brands on DEI gaps.

-   Evidence validates the need for data-driven website and analytics tracking.
:::

::: {.fragment .fade-up}
**Assessment & Affirmation of Analytics Objectives**

-   Objective aligns with business goals by positioning MAS as a credible inclusivity benchmark.

-   GA4-driven optimization improves conversions and client outreach.

-   Report downloads + blog content support lead generation.

-   A/B testing and heatmaps reinforce continuous UX improvement.
:::

## Measures

-   **MAS survey evaluates eight dimensions of Spanish-language accessibility:**

    -   Website accessibility

    -   App usability

    -   Phone customer service

    -   Promotions & prices

    -   Language clarity

    -   Visual appearance

    -   Conditions & warnings

    -   Follow-up emails

-   **Scored on a 0–100 scale (0 = poor experience; 100 = excellent experience).**

## **Analytics Methods to Employ**

**Analytics Objective #3: Conduct keyword-research analysis and explore GA4 data from the MAS website** to generate insights for SEO optimization, landing-page usability improvements, and content-engagement optimization.

::: {.fragment .fade-up}
**Method to Be Used**

-   Pre-launch keyword research using Ubersuggest for search demand analysis.

-   Post-launch GA4 tracking for:

    -   Traffic sources

    -   Landing-page performance

    -   Engagement + scroll depth

    -   User flow + drop-off points
:::

::: {.fragment .fade-up}
**Justification for the Method**

-   Keyword research ensures MAS content aligns with user search intent.

-   GA4 is standard for evaluating website performance and behavioral patterns.

-   Data will support decisions on content placement, messaging, and usability improvements.

-   Ensures MAS website resonates with B2C decision-makers seeking to improve DEI efforts.
:::

## **Variables to Be Used**

::: {.fragment .fade-up}
**Keyword Research Variables**

-   Keyword Research Variables

-   Search volume

-   Keyword difficulty

-   Competitiveness
:::

::: {.fragment .fade-up}
**GA4 Variables**

-   Organic traffic & acquisition channels

-   Search impressions

-   Bounce rate & engagement rate

-   Page views

-   Average session duration
:::

## Keyword Research Analysis

#### Load Packages and Initial Preparation

```{r}
#install.packages("gt")
#install.packages("gtExtras")

# Load libraries
library(gt)
library(gtExtras)
library(dplyr)
library(tidyr)
library(janitor)
library(readr)

```

```{r}
keywords <- read_csv("MAS Keyword Research.csv")
View(keywords)

#clean names
keywords <- keywords |>
  clean_names()

#remove $ and convert to numeric
keywords <- keywords |>
  mutate(cpc = as.numeric(gsub("\\$", "", cpc))) |>
  select(-no)

#summary
summary_labels <- c("Average", "Max", "Median", "Min")

```

#### Summary Statistics

```{r}
#Summary statistics
summary_stats <- keywords |>
  summarise(
    search_volume_mean   = mean(search_volume, na.rm = TRUE),
    search_volume_max    = max(search_volume, na.rm = TRUE),
    search_volume_median = median(search_volume, na.rm = TRUE),
    search_volume_min    = min(search_volume, na.rm = TRUE),

    cpc_mean             = mean(cpc, na.rm = TRUE),
    cpc_max              = max(cpc, na.rm = TRUE),
    cpc_median           = median(cpc, na.rm = TRUE),
    cpc_min              = min(cpc, na.rm = TRUE),

    paid_difficulty_mean   = mean(paid_difficulty, na.rm = TRUE),
    paid_difficulty_max    = max(paid_difficulty, na.rm = TRUE),
    paid_difficulty_median = median(paid_difficulty, na.rm = TRUE),
    paid_difficulty_min    = min(paid_difficulty, na.rm = TRUE),

    seo_difficulty_mean   = mean(seo_difficulty, na.rm = TRUE),
    seo_difficulty_max    = max(seo_difficulty, na.rm = TRUE),
    seo_difficulty_median = median(seo_difficulty, na.rm = TRUE),
    seo_difficulty_min    = min(seo_difficulty, na.rm = TRUE)
  )

```

```{r}
#Summary rows
summary_rows <- data.frame(
  keyword = c("Average", "Max", "Median", "Min"),
  search_volume = as.numeric(c(
    summary_stats$search_volume_mean,
    summary_stats$search_volume_max,
    summary_stats$search_volume_median,
    summary_stats$search_volume_min
  )),
  cpc = as.numeric(c(
    summary_stats$cpc_mean,
    summary_stats$cpc_max,
    summary_stats$cpc_median,
    summary_stats$cpc_min
  )),
  paid_difficulty = as.numeric(c(
    summary_stats$paid_difficulty_mean,
    summary_stats$paid_difficulty_max,
    summary_stats$paid_difficulty_median,
    summary_stats$paid_difficulty_min
  )),
  seo_difficulty = as.numeric(c(
    summary_stats$seo_difficulty_mean,
    summary_stats$seo_difficulty_max,
    summary_stats$seo_difficulty_median,
    summary_stats$seo_difficulty_min
  ))
)

```

#### Create Table

```{r}
#Combine and create a bar column (separate from numeric SEO difficulty) 
keywords_table <- bind_rows(keywords, summary_rows) |>
  mutate(
    is_summary = keyword %in% summary_labels,

    #This column is only for plotting bars
    seo_bar = if_else(is_summary, NA_real_, as.numeric(seo_difficulty))
  )

```

```{r}

#Table
keywords_table |>
  gt() |>
  tab_header(
    title = "Keyword Metrics",
    subtitle = "MAS Website Keyword Research"
  ) |>

  #Spanners
  tab_spanner(
    label = "METRICS",
    columns = c(search_volume, cpc, paid_difficulty, seo_difficulty, seo_bar)
  ) |>
  tab_spanner(
    label = "TRAFFIC",
    columns = c(search_volume)
  ) |>
  tab_spanner(
    label = "COMPETITION",
    columns = c(cpc, paid_difficulty, seo_difficulty, seo_bar)
  ) |>

  #Formatting: currency for CPC
  fmt_currency(
    columns = c(cpc),
    currency = "USD",
    decimals = 2
  ) |>

  #Keyword rows: whole numbers for metrics
  fmt_number(
    columns = c(search_volume, paid_difficulty, seo_difficulty),
    rows = !is_summary,
    decimals = 0
  ) |>

  #Summary rows: 2 decimals 
  fmt_number(
    columns = c(search_volume, paid_difficulty, seo_difficulty, cpc),
    rows = is_summary,
    decimals = 2
  ) |>

  #Bars column: show bar and number for keyword rows only
  gt_plt_bar(
    column = seo_bar,
    scaled = TRUE,
    text_labels = TRUE
  ) |>

  #Labels (make the bar col look like part of SEO difficulty)
  cols_label(
    keyword = "Keyword",
    search_volume = "Search Volume",
    cpc = "CPC",
    paid_difficulty = "Paid Difficulty",
    seo_difficulty = "SEO Difficulty",
    seo_bar = ""  
  ) |>

  # Hide helper column
  cols_hide(columns = is_summary) |>

  #Style summary rows 
  tab_style(
    style = list(
      cell_text(weight = "bold"),
      cell_fill(color = "white")
    ),
    locations = cells_body(rows = is_summary)
  ) |>

  tab_source_note(
    source_note = "Source: Keyword Research Analysis from Ubersuggest"
  )
```